Hybrid platforms and bargaining

### 2023-06-11 src/presentation/io_day.qmd
Minor improvements

::: {.fragment fragment-index=2}
 - The platform likes being hybrid
$$
\small
\frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0
$$
:::
::: {.fragment fragment-index=4}
 - It depends™ for the fringe
$$
\begin{align*}
\small\mathrm{sign} \left( \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} \right) = \\
\small\mathrm{sign} \left( \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} \right)
\end{align*}
$$
:::

@@

::: {.crossref .fragment}
Microfoundations: @sec-utility-function
:::

@@

::: {.incremental}
 - Total profits as a function of entrants have a simple form:
 $$
 f(N_P, N_F) = \mu \frac{N_F V_F + N_P V_P}{N_F V_F + N_P V_P + 1}
 $$
   - Satisfies the assumption for unique equilibrium
   - Has the form $f(N_P, N_F) = g(\alpha N_P + \beta N_F)$
   - $g$ is concave
 - Therefore,
 $$
 \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F}
 $$
:::

@@

::: {.fragment}
 - In this paper
   - Endogenenize hybridness ($N_P$)
   - Relax separate pricing assumption
   - Alternative benchmarks (e.g. exogeneous split)
:::
::: {.fragment}
 - Longer term
   - Endogeneize consumer entry (possibly with them engaging in the negotiation)
   - Apply this bargaining rule to other, similar settings
:::

>>>>

::: {.fragment fragment-index=2}
 - The platform likes being hybrid
   - It's profits increase in $N_P$
:::
::: {.fragment fragment-index=4}
 - It depends™ for the fringe
   - It's profits increase if and only if platform and fringe products are complements:
     $$ \scriptsize \frac{\partial f^2}{N_P N_F} > 0 $$
:::

@@

::: {.crossref .fragment}
Utility function: @sec-utility-function
:::

@@

::: {.incremental}
 - Total profits as a function of number of entrants have a simple form:
 $$
 f(N_P, N_F) = \mu \frac{N_F V_F + N_P V_P}{N_F V_F + N_P V_P + 1}
 $$
   - Satisfies the assumption for a unique equilibrium
   - Has the form $f(N_P, N_F) = g(\alpha N_P + \beta N_F)$
   - $g$ is concave
 - Therefore,
 $$
 \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F}
 $$
:::

@@

::: {.fragment}
 - In this paper
   - Endogenenize hybridness ($N_P$)
   - Relax separate pricing assumption
   - Alternative benchmarks (e.g. exogeneous split)
:::
::: {.fragment}
 - Longer term
   - Endogeneize consumer entry (possibly with consumers also engaging in the negotiation)
   - Apply this bargaining rule to other, similar settings
:::
